Weather Data MT

### 2024-03-20 qmd/pics/running/deadhorse.qmd
commit for 3/20

```{r eval = F, echo = F}
# Set the directory path
directory_path <- "img/deadhorse"

@@

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

@@

<div class="gallery">
<img src="img/deadhorse/deadhorse-top.JPG" alt="Image 1" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_0012.JPG" alt="Image 2" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_0016.JPG" alt="Image 3" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_0026.JPG" alt="Image 4" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6044.jpeg" alt="Image 5" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6050.jpeg" alt="Image 6" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6058.jpeg" alt="Image 7" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6061.jpeg" alt="Image 8" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6062.jpeg" alt="Image 9" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6067.jpeg" alt="Image 10" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6071.jpeg" alt="Image 11" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6078.jpeg" alt="Image 12" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6079.jpeg" alt="Image 13" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6080.jpeg" alt="Image 14" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6192.HEIC" alt="Image 15" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

>>>>

```{r eval = F, echo = F}
# Set the directory path
directory_path <- "img/deadhorse/"

@@

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', "../../../", directory_path, file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

@@

<div class="gallery">
<img src="../../../img/deadhorse/deadhorse-top.JPG" alt="Image 1" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_0012.JPG" alt="Image 2" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_0016.JPG" alt="Image 3" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_0026.JPG" alt="Image 4" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6044.jpeg" alt="Image 5" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6050.jpeg" alt="Image 6" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6058.jpeg" alt="Image 7" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6061.jpeg" alt="Image 8" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6062.jpeg" alt="Image 9" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6067.jpeg" alt="Image 10" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6071.jpeg" alt="Image 11" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6078.jpeg" alt="Image 12" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6079.jpeg" alt="Image 13" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6080.jpeg" alt="Image 14" onclick="expandImage(this)">
<img src="../../../img/deadhorse/IMG_6192.HEIC" alt="Image 15" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

### 2024-03-20 qmd/projects.qmd
commit for 3/20

  .text h1 {
    font-size: 18px; /* Adjusted text size */
    margin-top: 0;
    margin-bottom: 5px; /* Adjust margin between large and small text */
    color: black;
  }
  .text h1:hover {
    color: #2068DC; /* Change text color to blue on hover */
  }

  .text p {
    font-size: 14px;
    margin-top: 5px;
    color: #666;
    text-align: justify; /* Align text */
  }

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="msu-masters.qmd" class="container">
    <div class="image-container">
      <img src="img/projects-logos/msu-logo.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Montana State University Master's</h1>
        <p>Co-advised by Dr. David Weaver and Dr. Tracy Sterling.</p>
      </div>
    </div>
  </a>
  <a href="bballref.qmd" class="container">
    <div class="image-container">
      <img src="img/projects-logos/bballref-logo-circle.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>NBA Roster Analysis Tool</h1>
        <p></p>
      </div>
    </div>
  </a>
</body>
</html>

@@

>>>>

  .text h1 {
    font-size: 22px; /* Adjusted text size */
    margin-top: 0;
    margin-bottom: 5px; /* Adjust margin between large and small text */
    color: black;
  }
  .text h1:hover {
    color: #2068DC; /* Change text color to blue on hover */
  }

  .text p {
    font-size: 16px;
    margin-top: 5px;
    color: #666;
    text-align: justify; /* Align text */
  }

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="projects/msu-masters.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/msu-logo.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Montana State University Master's</h1>
        <p>2021-2024<br> Co-advised by Dr. David Weaver and Dr. Tracy Sterling</p>
      </div>
    </div>
  </a>
  <a href="projects/bballtool.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/bballref-logo-circle.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>NBA Roster Analysis Tool</h1>
        <p>2017-2019</p>
      </div>
    </div>
  </a>
</body>
</html>

@@

```{r, echo = F, message = F, results = 'hide'}
library(pandoc)
library(knitr)
library(rmarkdown)
getwd()
rmarkdown::render(input = "litreview.qmd", 
                  run_pandoc = TRUE,
                  output_format = "word_document")

### 2024-03-20 qmd/projects/msu-masters.qmd
commit for 3/20

---
title: "Projects"
editor_options: 
  chunk_output_type: console
---

@@

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="projects/msu-masters.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/msu-logo.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Montana State University Master's</h1>
        <p>2021-2024<br> Co-advised by Dr. David Weaver and Dr. Tracy Sterling</p>
      </div>
    </div>
  </a>
  <a href="projects/bballtool.qmd" class="container">
    <div class="image-container">
      <img src="../img/projects-logos/bballref-logo-circle.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>NBA Roster Analysis Tool</h1>
        <p>2017-2019</p>
      </div>
    </div>
  </a>
</body>
</html>

@@

```{r, echo = F, message = F, results = 'hide'}
library(pandoc)
library(knitr)
library(rmarkdown)
getwd()
rmarkdown::render(input = "litreview.qmd", 
                  run_pandoc = TRUE,
                  output_format = "word_document")

>>>>

---
title: "MSU Masters"

---

@@

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="msu-masters/wss.qmd" class="container">
    <div class="image-container">
      <img src="../../img/msu-masters/oviposition.JPG" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Wheat Stem Sawfly</h1>
        <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p>
      </div>
    </div>
  </a>
  <a href="msu-masters/locoweed/locoweed-report.qmd" class="container">
    <div class="image-container">
      <img src="../../img/msu-masters/loco-bee2.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Locoweed Volatiles</h1>
        <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p>
      </div>
    </div>
  </a>
  <a href="msu-masters/toadflax/toadflax_report.qmd" class="container">
    <div class="image-container">
      <img src="../../img/msu-masters/toadflax.jpeg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Toadflax</h1>
        <p></p>
      </div>
    </div>
  </a>
</body>
</html>

@@

### 2024-03-20 qmd/projects/msu-masters/locoweed/locoweed-report.qmd
commit for 3/20

---
title: "Locoweed Volatiles"
author: "Jackson Strand"
date: '`r format(Sys.Date())`'
output: 
  html_document:
    toc: true
    code_folding: hide
bibliography: citations/citations.bib
link-citations: true
cls: council-of-science-editors-author-date.csl
editor_options: 
  chunk_output_type: console
toc: true
---

@@

<div class="image-container">
    <img src="img/loco-bee-crop.JPG" alt="Your Image">
</div>

@@

# Set the directory path
directory_path <- "img/loco-plants"

@@

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

@@

<div class="gallery">
<img src="img/loco-plants/IMG_0064.jpg" alt="Image 1" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_0820 2.jpg" alt="Image 2" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1165.jpg" alt="Image 3" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1177.jpg" alt="Image 4" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1923.jpg" alt="Image 5" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

>>>>

---
title: "Locoweed Volatiles Report"
author: "Jackson Strand"
date: '`r format(Sys.Date())`'
output: 
  html_document:
    toc: true
    code_folding: hide
bibliography: locoweed.bib
link-citations: true
cls: council-of-science-editors-author-date.csl
editor_options: 
  chunk_output_type: console
toc: true
---

@@

<div class="image-container">
    <img src="../../../../img/loco-bee-crop.JPG" alt="Your Image">
</div>

@@

# Set the directory path
directory_path <- "../../../img/loco-plants"

@@

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', "../",directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

@@

<div class="gallery">
<img src="../../../../img/loco-plants/IMG_0064.jpg" alt="Image 1" onclick="expandImage(this)">
<img src="../../../../img/loco-plants/IMG_0820 2.jpg" alt="Image 2" onclick="expandImage(this)">
<img src="../../../../img/loco-plants/IMG_1165.jpg" alt="Image 3" onclick="expandImage(this)">
<img src="../../../../img/loco-plants/IMG_1177.jpg" alt="Image 4" onclick="expandImage(this)">
<img src="../../../../img/loco-plants/IMG_1923.jpg" alt="Image 5" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

### 2024-03-20 qmd/projects/msu-masters/wss.qmd
commit for 3/20

---
title: "MSU Masters"

---

@@

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="msu-masters/wss.qmd" class="container">
    <div class="image-container">
      <img src="../../img/msu-masters/oviposition.JPG" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Wheat Stem Sawfly</h1>
        <p>Understanding the importance of smooth brome in promoting a Braconid parasitoid that targets the Wheat Stem Sawfly.</p>
      </div>
    </div>
  </a>
  <a href="msu-masters/locoweed/locoweed-report.qmd" class="container">
    <div class="image-container">
      <img src="../../img/msu-masters/loco-bee2.jpg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Locoweed Volatiles</h1>
        <p>Comparison of volatile organic compounds profiles of <em>Oxytropis</em> plants that contained the commensal endophyte <em>Alternaria oxytropis</em> and those that did not.</p>
      </div>
    </div>
  </a>
  <a href="msu-masters/toadflax/toadflax_report.qmd" class="container">
    <div class="image-container">
      <img src="../../img/msu-masters/toadflax.jpeg" alt="Image">
    </div>
    <div class="content">
      <div class="text">
        <h1>Toadflax</h1>
        <p></p>
      </div>
    </div>
  </a>
</body>
</html>

>>>>

---
title: "MSU Master's: Wheat Stem Sawfly"
---

<a href="litreview.qmd" target="_blank">View Project Proposal</a>

@@

  @media (max-width: 768px) {
    .container {
      width: calc(100% - 20px); /* Adjusted width to fit the screen */
    }
  }
</style>
</head>
<body>
  <a href="wss/pfreport.qmd" class="container">
    <div class="image-container">
      <img src="../../../img/msu-masters/cages2.jpg" alt="Image"> 
    </div>
    <div class="content">
      <div class="text">
        <h1>Controlled WSS Infestation</h1>
        <p>Assessing WSS infestation and cutting within smooth brome in controlled research plot at Arthur H. Post Agronomy Farm.</p>
      </div>
    </div>
  </a>
  <a href="wss/field_report.qmd" class="container">
    <div class="image-container">
      <img src="../../../img/msu-masters/oviposition.JPG" alt="Image"> 
    </div>
    <div class="content">
      <div class ="text">
        <h1>Montana Field Sites</h1>
        <p>Collection of wheat and smooth brome in Big Sandy and Moccasin, Montana to assess parasitism and WSS infestation.</p>
      </div>
    </div>
  </a>
  <a href="wss/eag.qmd" class="container">
    <div class="image-container">
      <img src="../../../img/msu-masters/vcs.jpg" alt="Image"> 
    </div>
    <div class="content">
      <div class="text">
        <h1>Organic Volatile Collection</h1>
        <p>Collection of wheat and smooth brome in <strong>Big Sandy</strong> and <strong>Moccasin</strong> Montana to assess parasitism and WSS infestation.</p>
      </div>
    </div>
  </a>
  <a href="wss/weatherdata.qmd" class="container">
    <div class="image-container">
      <img src="../../../img/msu-masters/clouds.jpg" alt="Image"> 
    </div>
    <div class="content">
      <div class="text">
        <h1>Weather Data</h1>
        <p>Weather data trends from Big Sandy and Moccasin, Montana.</p>
      </div>
    </div>
  </a>
</body>
</html>

### 2024-03-20 qmd/projects/msu-masters/wss/weatherdata.qmd
commit for 3/20

ggplot(data = bozeman_weather) +
  geom_line(aes(x = date, y = TMAX)) +
  theme_bw()
```
title: "Montana Weather Data"
---

>>>>

ggplot(data = bozeman_weather) +
  geom_line(aes(x = date, y = PRCP)) +
  theme_bw()

ggplot(data = bozeman_weather) +
  geom_line(aes(x = date, y = PRCP)) +
  geom_smooth(aes(x = date, y = PRCP), method = "loess", se = TRUE) +
  theme_bw()

```
title: "Montana Weather Data"
---
